### 2023-01-26 paper-reviews/papers-2023.tex
Add Philips VLIW report
Add multiflow VLIW paper

    \cite{Dall:KVM-ARM:2014}
\end{itemize}

@@

    \cite{Demler:Helios:2019}
\end{itemize}

@@

    \cite{Regehr:C-Reduce:2012}
\end{itemize}

>>>>

    \cite{Dall:KVM-ARM:2014}.
\end{itemize}

@@

    \cite{Demler:Helios:2019}.
\end{itemize}

@@

    \cite{Regehr:C-Reduce:2012}.
\end{itemize}

\section*{Computer Architecture}
\begin{itemize}
    \item Nice high level overview of VLIW architecture and comparison with typical RISC and CISC designs. Great reference for students to show the basic concepts of CPU architectures even though it is not fully relevant anymore:

    \cite{Philips:VLIW:1997}.

    \item The paper describes a VLIW architecture developed by Multiflow Corporation. It is one of the VLIW pioneering designs. It is always enjoyable to read old papers about computer architecture trends and ideas; compare the old ideas and expectations with how it turned out now: <<a VLIW machine was expected to provide from ten to thirty times the performance of a more conventional machine built of the same implementation technology>>. A great comments for the citation would be something like: <<if only we would have smart enough compiler>>. Industry practice so far showed that VLIW could be an amazing architecture for some DSPs while a superscalar processor delivers better results for general purpose usage:

    \cite{Colwell:Multiflow-VLIW:1987}.
\end{itemize}
